Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-16 docs/manuscript/manuscript.tex
Updates from Overleaf

\begin{table}[h!]
    \centering
    \begin{tabular}{l l l}\toprule
    \bf Scenario            & \bf Description  & \bf No.\ classes\\\midrule
    \texttt{Pr\_Po\_Im}     &  \{Probable, Possible, Improbable\} & 3 \\
    \texttt{Pr\_Im}          & \{Probable, Improbable\}           & 2 \\
    \texttt{PrPo\_Im}        & \{Probable|Possible, Improbable\}  & 2 \\
    \texttt{Pr\_PoIm}        & \{Probable, Possible|Impossible\}  & 2 \\\bottomrule
    \end{tabular}
    \caption{Classification scenarios}
    \label{tab:scenarios}
\end{table}

\subsection{Pre-processing and data augmentation}
To achieve robustness in training, and given the relatively small number of training images, we randomly cropped each image on either axis to 3024 $\times$ 3024 pixels, generating five instances for each one. Thus, we increased the size of our training set from 505 to 2525 images. Further, we performed horizontal flipping with a 50\% probability on each of the generated images. For efficiency, we converted the images to grayscale and scaled the pixel values from 0 to 1. Finally, we downsampled the images to the following resolutions: $64 \times 64$, $128 \times 128$, $224 \times 224$ and $384\times 384$, creating a training set for each case. 
Random sets of images from each class across each of the four classification scenarios are shown in \autoref{fig:processed_images}.

@@

\begin{table}[h!]\small
    \centering
    \begin{tabular}{|l | l l l l| l l l l| l l l l | l l l l|}\hline
    %\bf Scenario 
        &  \multicolumn{4}{c|}{\texttt{Pr\_Po\_Im}} 
            & \multicolumn{4}{c|}{\texttt{Pr\_Im}} 
                &  \multicolumn{4}{c|}{\texttt{PrPo\_Im}} 
                    &  \multicolumn{4}{c|}{\texttt{Pr\_PoIm}}  \\\hline
    %\bf Resolution
        & 64 & 128 & 224 & 384 
            & 64 & 128 & 224 & 384 
                & 64 & 128 & 224 & 384
                    & 64 & 128 & 224 & 384  \\\hline
    %\bf Hyperparameter 
    $ks$    &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $u_1$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $d_1$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $a_1$   & ReLu  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $u_2$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\ 
    $d_2$   &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $a_2$   & ReLu &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\
    $\lambda$  
            &  &  &  &  &   &  &  &  &   &  &  &  &   &  &  &   \\\hline
    \end{tabular}
    \caption{Optimal hyperparameters found using the Hyperband search algorithm for all classification scenario and input image resolution combinations.}
    \label{tab:opt-hyp}
\end{table}
\section{Results}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{l l c}\toprule
    \bf Scenario            & \bf Description  & \bf No.\ classes\\\midrule
    \texttt{Pr\_Po\_Im}     &  \{Probable, Possible, Improbable\} & 3 \\
    \texttt{Pr\_Im}          & \{Probable, Improbable\}           & 2 \\
    \texttt{PrPo\_Im}        & \{Probable|Possible, Improbable\}  & 2 \\
    \texttt{Pr\_PoIm}        & \{Probable, Possible|Impossible\}  & 2 \\\bottomrule
    \end{tabular}
    \caption{Classification scenarios}
    \label{tab:scenarios}
\end{table}

\subsection{Pre-processing and data augmentation}
To achieve robustness in training, and given the relatively small number of training images, we randomly cropped each image on either axis to 3024 $\times$ 3024 pixels, generating five instances for each one. Thus, we increased the size of our training set from 505 to 2525 images. Further, we performed horizontal flipping with a 50\% probability on each of the generated images. For efficiency, we converted the images to grayscale and scaled the pixel values from 0 to 1. Finally, we downsampled the images to the following resolutions (pixels): $64 \times 64$, $128 \times 128$, $224 \times 224$ and $384\times 384$, creating a training set for each case. 
Random sets of images from each class across each of the four classification scenarios are shown in \autoref{fig:processed_images}.

@@

\begin{table}[h!]\small
    \centering
    \begin{tabular}{l  c  p{1.75cm} p{1.75cm}  p{1.75cm} p{1.75cm}}\toprule
    \bf Scenario & \bf Hyperparameter & \multicolumn{4}{c}{\bf Resolution ($n\times n$ pixels)} \\
    &         & 64 & 128 & 224 & 384 \\\midrule
    \multirow{8}{*}{\texttt{Pr\_Po\_Im}} 
        & $ks$    & 7 &  &  &   \\
        & $u_1$   & 128 &  &  &   \\
        & $d_1$   & 0.25 &  &  &   \\
        & $a_1$   & ReLu  &  &  &   \\
        & $u_2$   & 320 &  &  &   \\
        & $d_2$   & 0.30 &  &  &   \\
        & $a_2$   & ReLu &  &  &   \\
        & $\lambda$  & $1.76\cdot 10^{-4}$ &  &  &   \\ \midrule
    \multirow{8}{*}{\texttt{Pr\_Im}} 
        & $ks$    & 7 &  &  &   \\
        & $u_1$   & 128 &  &  &   \\
        & $d_1$   & 0.25 &  &  &   \\
        & $a_1$   & ReLu  &  &  &   \\
        & $u_2$   & 320 &  &  &   \\
        & $d_2$   & 0.30 &  &  &   \\
        & $a_2$   & ReLu &  &  &   \\
        & $\lambda$  & $1.76\cdot 10^{-4}$ &  &  &   \\ \midrule
    \multirow{8}{*}{\texttt{PrPo\_Im}} 
        & $ks$    & 7 &  &  &   \\
        & $u_1$   & 128 &  &  &   \\
        & $d_1$   & 0.25 &  &  &   \\
        & $a_1$   & ReLu  &  &  &   \\
        & $u_2$   & 320 &  &  &   \\
        & $d_2$   & 0.30 &  &  &   \\
        & $a_2$   & ReLu &  &  &   \\
        & $\lambda$  & $1.76\cdot 10^{-4}$ &  &  &   \\ \midrule
    \multirow{8}{*}{\texttt{Pr\_PoIm}}  
        & $ks$    & 7 &  &  &   \\
        & $u_1$   & 128 &  &  &   \\
        & $d_1$   & 0.25 &  &  &   \\
        & $a_1$   & ReLu  &  &  &   \\
        & $u_2$   & 320 &  &  &   \\
        & $d_2$   & 0.30 &  &  &   \\
        & $a_2$   & ReLu &  &  &   \\
        & $\lambda$  & $1.76\cdot 10^{-4}$ &  &  &   \\ \bottomrule
    \end{tabular}
    \caption{Optimal hyperparameters found using the Hyperband search algorithm for all classification scenario and input image resolution combinations.}
    \label{tab:opt-hyp}
\end{table}
\section{Results}
